Delta Factor - A New Authorization Factor

### 2022-08-09 paper1.tex
Update paper1.tex
Tiny typos complete.

\subsubsection{Should not be a Solo Factor}
COTP provides a robust method to validate multiple factors, namely: knowledge, connection details, and device. However, for maximum effectiviness, validation of both parties should be done. First, the user should be validated by the server - ideally using COTP or another 2FA method. This is the same as the state of the art today by Duo or Google Authenicator. But, an additional validation should be used to allow the client to validate the server. Because the server has already validated the client, this is effectively a courtesy offered and as no impact on authorization to access the protected resources.

\subsubsection{Connection Latency Reporting May Vary}
This work offers a method to deal with latency mismatch between server and client by rounding to the nearest prime based latency window. Multiple COTPs should be done through the client or simply retrying authenication as propsed in this work. However, this method means that a stocastic method to validating the user should be used to reduce the number of retries. This is in contrast to a traditional one-time password methods, which can be performed from a seperate device.

@@

Another potiential future work is finding the optimal balance between connection oriented details and other factors. This work focused on introducing connection oriented features to a verification algorithm, using only shared features between both parties; however, there are additional features that are shared, and can be included. One such additional feature is each party's supported cipher suites or another is selected curve - both could increase difficultly for an advanced transparent MITM to sucessfully mimick all details symetrically. However, the increase in difficultly also needs to be assessed. Another issue is balance between authication features - a completely connection oriented approach will fail, due to connection details being publically available to a motivated attacker through protocol analysis.

Finally, another future work is potientially repeatedly validating or checking factors periodically. TLS addresses forward secrecy through rekeying - and this is part of the protocol. The same process could trigger a transparent COTP generation and exchange. This type of feature is already possible on the browser side and could be implemented on the server side. In addition, a new shared secret could be generated, and shared upon rekey - allowing a forward autheication. Those with access to previous details would not have future authenication.

>>>>

\subsubsection{Should not be a Solo Factor}
COTP provides a robust method to validate multiple factors, namely: knowledge, connection details, and device. However, for maximum effectiviness, validation of both parties should be done. First, the user should be validated by the server - ideally using COTP or another 2FA method. This is the same as the state of the art today by Duo or Google Authenticator. But, an additional validation should be used to allow the client to validate the server. Because the server has already validated the client, this is effectively a courtesy offered, and has no impact on authorization to access the protected resources.

\subsubsection{Connection Latency Reporting May Vary}
This work offers a method to deal with latency mismatches between the server and the client by rounding to the nearest prime based latency window. Multiple COTPs should be done through the client, or, simply retrying authentication as proposed in this work. However, this method means that a stochastic method to validating the user should be used to reduce the number of retries. This is in contrast to traditional one-time password methods, which can be performed from a seperate device.

@@

Another potiential future work is finding the optimal balance between connection oriented details and other factors. This work focused on introducing connection oriented features to a verification algorithm. This is by using only shared features between both parties, however there are additional features that are shared, which can be included. One such additional feature is each party's supported cipher suite, or, another is the selected curve - and both could increase difficultly for an advanced transparent MITM to sucessfully mimick all details symetrically. However, the increase in difficultly also needs to be assessed. Another issue is balance between authentication features, ie., a completely connection-oriented approach will fail, due to connection details being publically available to a motivated attacker through protocol analysis.

Finally, another future work is potientially repeatedly validating or checking factors periodically. TLS addresses forward secrecy through rekeying, and this happens to be part of the protocol. The same process could trigger a transparent COTP generation and exchange. This type of feature is already possible on the browser side, and could be implemented on the server side as well. In addition, a new shared secret could be generated and shared upon rekeying, forward authentication is allowed. Those with access to previous details would not have future authentication.
